Mixture distribution data generation

### 2022-02-15 Ch3_samplesize/Ch3_Figures.Rmd
Figures.

resamp.df %>% 
  mutate(diff = (cdfs.hat-true.cdfs), 
         sampsize = factor(all.sampsizes),
         tailthresh = factor(all.qtests))-> resamp.df

resamp.df %>% 
  #filter(., all.sampsizes == "80") %>%  
  ggplot(., aes(x = sampsize, y = diff, color = tailthresh)) +
  geom_boxplot() +
  labs(x = "Sample size", y = "Estimated/True") +
  #scale_y_log10() +
  theme_minimal()

@@

We want to know how "off" the estimates are from the truth.
```{r}
resamp.df %>% 
  group_by(sampsize, tailthresh) %>% 
  summarise(est.bias = signif(mean(diff), 3))

resamp.df %>% 
  group_by(sampsize, tailthresh) %>% 
  summarise(est.bias = signif(mean(diff), 3)) %>% 
  ggplot(., aes(x = sampsize, color = tailthresh, y = est.bias)) +
  geom_point() +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()

@@

### Now, let's simulate the individuals

>>>>

resamp.df %>% 
  mutate(diff = (cdfs.hat-true.cdfs),
         est.over.true = cdfs.hat/true.cdfs,
         sampsize = factor(all.sampsizes),
         tailthresh = factor(all.qtests))-> resamp.df

resamp.df %>% 
  #filter(., all.sampsizes == "80") %>%  
  ggplot(., aes(x = sampsize, y = est.over.true, color = tailthresh)) +
  geom_boxplot() +
  labs(x = "Sample size", y = "Estimated/True") +
  #scale_y_log10() +
  theme_minimal()

@@

We want to know how "off" the estimates are from the truth.
```{r}

resamp.df %>% 
  group_by(sampsize, tailthresh) %>% 
  summarise(mean.diff = signif(mean(diff), 3)) %>% 
  ggplot(., aes(x = sampsize, color = tailthresh, y = mean.diff)) +
  geom_point() +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()

@@

### Should I simulate the individuals
